### 2019-02-28 sections/introduction.tex
Fixed nits in introduction

% Task-Oriented Programming (\TOP) is a programming paradigm aimed at writing interactive multi-user applications in a declarative way \cite{conf/ppdp/PlasmeijerLMAK12}.
Task-oriented programming (\TOP) is a programming paradigm which targets the sweet spot between faithful modelling workflows
and rapid prototyping of multi-user web applications supporting these workflows \cite{conf/ppdp/PlasmeijerLMAK12}.
% Task-oriented programming (\TOP) is a programming paradigm to support these ways of working.
\TOP focusses on modelling collaboration patterns.
This gives rise to user's need to interact and share information.
Next to that, \TOP automatically provides solutions to common development jobs like designing \GUI\ s, connecting to databases, and communicating between servers and clients.

@@

% \ITASKS is the de-facto reference implementation of \TOP.
Both \ITASKS and \MTASKS have been designed for developing real-world applications.
They are constantly being extended and improved with this goal in mind.
The different variations of task combinators and the details that come with real-world requirements,
make it hard to see what the essence of \TOP is.
% One of the defining aspects of both \ITASKS and \MTASKS is their embedding in a functional programming language.
% This creates a synergy where they profit from the expressivity of Clean, while enhancing the language with functionality for user interaction.
Also, the tight integration of both frameworks with the Clean, makes it difficult to see where the boundaries are.
This makes formal reasoning about \TOP programs impossible.

In this paper, we want to take a step back and look at the spirit of \TOP.
We do this both formally and informally.
Informally in the sense that we give an intuitive description of the features that define task-oriented programming.
Formally in the sense that we develop a calculus which formalises these features as language constructs,
and we give them semantics in the style that is common in programming language research.
We separate the task layer and the underlying host language, both syntactically and semantically.
Thus making explicit which properties of \TOP come from the task layer, and which come from functional programming.
Our challenge, therefore, is to model the properties of \TOP into a calculus
and, pave the way for formal treatment of \TOP programs.
We give this formal calculus the name \TOPHAT (TopHat).

>>>>

% Task-Oriented Programming (\TOP) is a programming paradigm aimed at writing interactive multi-user applications in a declarative way \cite{conf/ppdp/PlasmeijerLMAK12}.
Task-oriented programming (\TOP) is a programming paradigm which targets the sweet spot between faithful modelling workflows
and rapid prototyping of multi-user web applications supporting these workflows \cite{conf/ppdp/PlasmeijerLMAK12}.
% Task-oriented programming (\TOP) is a programming paradigm to support these ways of working.
\TOP focusses on modelling collaboration patterns.
This gives rise to a user's need to interact and share information.
Next to that, \TOP automatically provides solutions to common development jobs like designing \GUI{s}, connecting to databases, and communicating between servers and clients.

@@

% \ITASKS is the de-facto reference implementation of \TOP.
Both \ITASKS and \MTASKS have been designed for developing real-world applications.
They are constantly being extended and improved with this goal in mind.
The different variations of task combinators and the details that come with real-world requirements,
make it hard to see what the essence of \TOP is.
% One of the defining aspects of both \ITASKS and \MTASKS is their embedding in a functional programming language.
% This creates a synergy where they profit from the expressivity of Clean, while enhancing the language with functionality for user interaction.
Also, the tight integration of both frameworks with Clean, makes it difficult to see where the boundaries are.
This makes formal reasoning about \TOP programs impossible.

In this paper, we want to take a step back and look at the spirit of \TOP.
We do this both formally and informally.
Informally in the sense that we give an intuitive description of the features that define task-oriented programming.
Formally in the sense that we develop a calculus which formalises these features as language constructs,
and we give them a semantics in the style that is common in programming language research.
We separate the task layer and the underlying host language, both syntactically and semantically.
Thus making explicit which properties of \TOP come from the task layer, and which come from functional programming.
Our challenge, therefore, is to model the properties of \TOP into a calculus
and pave the way for formal treatment of \TOP programs.
We give this formal calculus the name \TOPHAT (TopHat).
